Leaf traits drive differences in above-ground biomass distribution among major plant functional types

### 2015-11-06 manuscript.Rnw
Figures are updated.

\section*{Revision notes}
\begin{enumerate}
\item Reduce focus on GVMs in introduction (Reviewer 2).
\item Better linking to Poorter 2015 and Reich 2014 (editor, reviewer 2, reviewer 3, poorter pers comm).
\item Remove LMF and LAR, and only analyze MF/MS and AF/MS. This avoids confusion of the terms LMF and LAR which normally include root biomass. We should more clearly focus on above-ground biomass distribution patterns (editor + reviewer 2).
\item Partition variance in MF/MS directly, not the proxy variable MF/AS. We did that for statistical convenience, as reviewer 1 is correct in pointing out. But we can look at partitioning variance in MF/MS directly, to plant height, PFT and climate. Reviewer 3 (though incorrectly) says 'also have the same variable in the numerator and denominator, which causes statistical issues' - but then we can say we avoid this apparent problem.
\item We claim that climate does not affect biomass distribution, but reviewer 1 correctly points out that climate affects plant height, so it may have an indirect effect. Our dataset is not appropriate for testing effects of climate on typical (or maximum) plant height, because individuals of all kinds of sizes were sampled; there will be sampling bias. Moles et al. 2009 reported that maximum plant height shows a strong latitudinal pattern (taller plants at low latitude), and is correlated with climate variables. We just have to describe their results.
\item Can follow reviewer 1's suggestion to partition MF/MS like this: $\frac{M_F}{M_S} = \frac{A_F}{A_S}\frac{M_F}{A_F}\frac{A_S}{M_S}$
\item Reviewer 2 has some strange comments about MS/AS, in that we expect them to be correlated. Yes, but we need to make the point more clearly that there could be PFT effects in this correlation, largely through wood density (and tree shape). In fact we bring this up, but partitioning the variance as above may make this stand out more.
\item "The methods do not describe if the individual data points came from trees in closed-canopy or open stands.  That would also make a huge difference." (Reviewer 3)
\end{enumerate}

>>>>

\section*{Revision notes}
\begin{enumerate}
\item Reduce focus on GVMs in introduction (Reviewer 2).
\item Better linking to Poorter 2015 and Reich 2014 (editor, reviewer 2, reviewer 3, poorter pers comm).
\item Remove LMF and LAR, and only analyze MF/MS and AF/MS. This avoids confusion of the terms LMF and LAR which normally include root biomass. We should more clearly focus on above-ground biomass distribution patterns (editor + reviewer 2).
\item Partition variance in MF/MS directly, not the proxy variable MF/AS. We did that for statistical convenience, as reviewer 1 is correct in pointing out. But we can look at partitioning variance in MF/MS directly, to plant height, PFT and climate. Reviewer 3 (though incorrectly) says 'also have the same variable in the numerator and denominator, which causes statistical issues' - but then we can say we avoid this apparent problem.
\item We claim that climate does not affect biomass distribution, but reviewer 1 correctly points out that climate affects plant height, so it may have an indirect effect. Our dataset is not appropriate for testing effects of climate on typical (or maximum) plant height, because individuals of all kinds of sizes were sampled; there will be sampling bias. Moles et al. 2009 reported that maximum plant height shows a strong latitudinal pattern (taller plants at low latitude), and is correlated with climate variables. We just have to describe their results.
\item Can follow reviewer 1's suggestion to partition MF/MS like this: $\frac{M_F}{M_S} = \frac{A_F}{A_S}\frac{M_F}{A_F}\frac{A_S}{M_S}$
\item Reviewer 2 has some strange comments about MS/AS, in that we expect them to be correlated. Yes, but we need to make the point more clearly that there could be PFT effects in this correlation, largely through wood density (and tree shape). In fact we bring this up, but partitioning the variance as above may make this stand out more.
\item "The methods do not describe if the individual data points came from trees in closed-canopy or open stands.  That would also make a huge difference." (Reviewer 3)
\item We used MAT, MAP as well as the interaction. Probably better climate variables out there, but having the interaction in a model does distinguish between warm-dry and warm-wet climates (just like aridity indices). Because we found no appreciable effects of climate, we did not think it was worthwhile testing all possible climate variables.
\end{enumerate}
